---
title: "Introduction to cleanr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cleanr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(cleanr)
```

## Why cleanr?

When you first open a real dataset, you almost always run into the same
problems: missing values, messy column names, and weird extreme numbers.
cleanr gives you three simple functions to deal with all of that quickly.

## The Sample Dataset

cleanr comes with a built-in dataset called `messy_data` that has all
three problems so you can practice.

```{r}
messy_data
```

## Step 1 — Find the Missing Values

```{r}
describe_na(messy_data)
```

This shows you exactly which columns have missing data and how much.

## Step 2 — Clean the Column Names

```{r}
clean <- standardize_names(messy_data)
names(clean)
```

Now all names are lowercase with underscores, so they are easy to type.

## Step 3 — Remove Outliers

The salary of one billion is clearly wrong. We can remove it using
the IQR method:

```{r}
clean <- remove_outliers(messy_data, col = "salary", method = "iqr")
clean
```

## Full Workflow in One Go

```{r}
result <- messy_data |>
  remove_outliers(col = "salary", method = "iqr")

describe_na(result)
```
